Genome-wide changes in expression during inflorescence architecture development

### 2015-09-14 ms.Rmd
Cleaned up script for selection by clade

The primary sequences of *Arabidopsis thaliana*, *Solanum lycopersicum* and *Oryza sativa* MADS proteins were downloaded by querying Phytozome 10.3 [@Goodstein:2012ho] for the PANTHER family PTHR11945 ('MADS BOX PROTEIN') via the `biomaRt` interface [@Thomas:2003db; @Durinck:2009ki].

>>>>

The primary sequences of *Arabidopsis thaliana*, *Solanum lycopersicum* and *Oryza sativa* MADS proteins were downloaded by querying Phytozome 10.3 [@Goodstein:2012ho] for the PANTHER family PTHR11945 ('MADS BOX PROTEIN') via the `biomaRt` interface [@Thomas:2003db; @Durinck:2009ki]. An initial alignment of all proteins was performed with `Clustal Omega` using a full distance matrix (**ref clustalo**). To clean the alignment, poorly conserved regions where greater than `minpcnongap` percent of sequences had gaps or less than `minpcident` perc ent of pairwise comparisons between sequences had identical residues were removed. To recover MADS genes related to the Arabidopsis MIKC clade, a UGPMA tree was estimated from the cleaned alignment and the tree was cut at the lowest height that returned a clade including all type II Arabidopsis MADS proteins listed in the Arabidopsis transcription factor database on the Arabidopsis Gene Regulatory Information Server (**ref for AGRIS**), with as few type I proteins as possible. Protein sequences in this clade that were longer than `minProtLength` amino acids were realigned using `Clustal Omega`, and the alignment was cleaned as described above, used to estimate a neighbour-joining tree with the `bionj` algorithm implemented in the `ape` package (**ref:ape***) and rooted to a type I MADS sequence (`og`). The tree was plotted using the `ggtree` extension for `ggplot2` (**ref ggtree**).
